Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-20 ICML-submission/notions-of-linear-separability.tex
Update notions-of-linear-separability.tex
Moved the discussion on the Multiclass Perceptron lower bound to Section 1 from here.

The notion of weak linear separability is a standard assumption used in the
full-information setting to upper bound the number of mistakes of the
\textsc{Multiclass Perceptron} algorithm. Namely, \citet{Crammer-Singer-2003}
prove that if the examples are weakly linearly separable with a margin $\gamma$
and the norm of the examples is bounded by $R$, then \textsc{Multiclass
Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
mistakes. It is a folklore result that \textsc{Multiclass Perceptron} is
essentially optimal in the sense that any (possibly randomized) algorithm must
make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
worst case. For completeness, we state the \textsc{Multiclass Perceptron}
algorithm and give proofs of both of these results in
Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
material.

>>>>

The notion of weak linear separability is a standard assumption used in the
full-information setting to upper bound the number of mistakes of the
\textsc{Multiclass Perceptron} algorithm.
%%%%%
(Recall our discussion on the topic in Section~\ref{section:introduction}.)
%Namely, \citet{Crammer-Singer-2003}
%prove that if the examples are weakly linearly separable with a margin $\gamma$
%and the norm of the examples is bounded by $R$, then \textsc{Multiclass
%Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
%mistakes. It is a folklore result that \textsc{Multiclass Perceptron} is
%essentially optimal in the sense that any (possibly randomized) algorithm must
%make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
%worst case. For completeness, we state the \textsc{Multiclass Perceptron}
%algorithm, the upper and lower bound on the number of mistakes, and their proofs
%in Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
%material.
%%%%%
